Making Sequential Programs Deterministic

### 2019-04-06 design.tex
Edits on pages 6 and 7

  Basetype polymorphism is rarely used on its own.  Full type polymorphism is more
  common, even if the type is decomposed and the parts used independently,
  as in this more general type for the \<choose> function:

@@

The body of \<length> must typecheck at every possible instantiation of its
polymorphic function type.  At a use site of \<length>,
the most specific applicable instantiation is chosen.
Here is an example:

Suppose we have two variables $\<ni> : \<NonDet Int>$ and $\<di> : \<Det Int>$.
This table shows, for several method invocations, the 
most specific applicable instantiation for that invocation and the type of
the call expression:

@@

We adopt the convention that  polymorphism is not instantiated in ways
that would create invalid types.  For example, the \<length> and \<plus> polymorphic
functions would not be instantiated at $\kappa = \<OrderNonDet>.$
This makes no difference for these particular functions:  such an
instantiation would never be the most specific applicable one.
This is important for some of the type rules given in this paper, which
would otherwise need complex preconditions that recapitulate the type
well-formedness rules.

@@

\noindent
because such an instantiation would include the invalid return type \<OrderNonDet Int>.
This means that the only two instantiations are at 
$\kappa = \<NonDet>$ and $\kappa = \<Det>$.  An invocation on an
\<OrderNonDet> collection would choose the \<NonDet> instantiation and the
return type at that call site would be \<NonDet Int> rather than the
desired \<Det Int>.

>>>>

  Basetype polymorphism is rarely used on its own.  Full type polymorphism is more
  common, even if the function type decomposes the type parameter and uses the parts independently,
  as in this more general type for the \<choose> function:

@@

\noindent
The body of \<length> must typecheck at every possible instantiation of its
polymorphic function type.  At a use site of \<length>,
the most specific applicable instantiation is chosen.

For example,
suppose we have two variables $\<ni> : \<NonDet Int>$ and $\<di> : \<Det Int>$.
This table shows, for several method invocations, the 
most specific applicable instantiation for that invocation and the type of
the call expression:

@@

We adopt the convention that  polymorphism is not instantiated in ways
that would create invalid types.  For example, the \<length> and \<plus> polymorphic
functions would not be instantiated at $\kappa = \<OrderNonDet>.$
This makes no difference for these particular functions:  such an
instantiation would never be the most specific applicable one.
The general rule about instantiations and type validity
is important for some of the type rules given in this paper, which
would otherwise need complex preconditions that recapitulate the type
well-formedness rules.

@@

\noindent
because such an instantiation would include the invalid return type \<OrderNonDet Int>.
This means that the only two instantiations are at 
$\kappa = \<NonDet>$ and $\kappa = \<Det>$.  An invocation on an
\<OrderNonDet> collection would choose the \<NonDet> instantiation, and the
return type at that call site would be \<NonDet Int> rather than the
desired \<Det Int>.
